\documentclass[12pt]{article}
\usepackage{nopageno}
\usepackage{xcolor} % for different colour comments
\usepackage{parskip} % Space between each paragraph.
\usepackage{hardwrap} % for text length of 80 pts
\usepackage[margin=1.2in]{geometry}
%\usepackage{../ltx/edcomms}

%\input{../ltx/setupComments}

\setlength{\parindent}{15pt} % parskip sets this to 0. 15 is default.

%%%%%%%%%%%%%%%	START OF DOCUMENT %%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{CS4ZP6 Test Plan \\ Ampersand Tarski Event-Condition-Action 
Rules \\ \vspace{-1ex}} 
\author{\normalsize{Yuriy Toporovskyy,\ Yash Sapra,\ Jaeden Guo}}
\date{\normalsize\today \vspace{-3ex}}
\thispagestyle{empty}
\maketitle
\paragraph{}
The focus of the test plan will be to demonstrate the current state of 
Ampersand model prior to the addition of our project and to provide an overview 
of where our project fits into the Ampersand system. Ampersand will be 
presented as a system with patches for its unfinished pieces and one of those 
missing pieces is the purpose of our project, EFA. Although Ampersand is 
functional it is limited on the number of finished products and complete 
services it can provide for/to its user. An example script will be compiled 
using Ampersand and multiple switches (i.e. compilation options) which 
generates different user feedback and creates various Ampersand artifacts. 
\newline
\indent This demonstration will be a black box test of the current Ampersand 
system, 
the example will produce various kinds of errors and violations. The errors 
produced are handled by the Amperand system; the error outputs the user 
receives are meant to inform the user of syntax and context or environmental 
errors such as a missing definition for a variable. Violations inform the user 
when the process they are attempting to simulate violates the rules they have 
set in place in system. An example of this is if a theatre is hiring 
actors/actresses to play a role, the rule is that only actors/actresses who 
have a sufficient amount of experience can play lead. The user  can define a 
‘sufficient amount of experience’ to be anything they wish, from the number of 
plays the individual has been casted in, to the years that actor(ess) has 
worked in the industry. A violation of the rule would be attempting to cast an 
actor into a leading role who has not met the conditions of a ‘sufficient 
amount of experience’. 
\newline
\indent The purpose of the EFA project is to automate the correction of a 
particular 
class of violations that restores invariants with in the Ampersand system. 
These violations come from the misuse of PAClauses (Process Algebra Clauses); 
PAClauses are datatypes formed from ECA (Event-Condition Action) rules used to 
represent the structure of an active database system. In Ampersand, these ECA 
rules are decomposed to their most basic forms which we call, Atoms. Atoms are 
the simplest possible form a rule can take before losing its meaning. From 
here, a Haskell program (i.e., EFA) will automate the correction of violations 
by detecting contradictions between Atoms imposed on datasets. For example, one 
Atom can state that all entities in its set must be blue, another Atom states 
that all entities in its set must be red. The intersection between these two 
Atoms is red AND blue, if the user inserts something in the intersection of red 
and blue that is not red and blue, it is a violation of both atoms. A quick fix 
to restore both rules would be to remove the entity that is not red or blue 
from the intersection of the red and blue set. 
\newline
\indent EFA is in its initial stages of development, and at this time it is 
difficult 
to provide a rigorous guide as to how this project will proceed. The first step 
was to figure out the particular classes of violations and the most 
conventional ways they are triggered. From there the developers of Ampersand 
have provided a partial algorithm for how individual violations can be 
restored. Foreseeable issues include not having a complete algorithm to 
implement on complex system such as Ampersand, in addition to figuring out how 
to fix violations that may cycle within itself.

\end{document}










