\documentclass[12pt, svgnames]{article}

\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage[round,numbers]{natbib}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{../ltx/edcomms}
%%\usepackage{../ltx/setupComments}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{changepage}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage[section]{placeins} % Prevents floats from floating across sections
\usepackage{tabularx}
\usepackage{amsfonts}
\usepackage{glossaries}
\usepackage{multirow} %% Used for Traceability matrix
\usepackage{listings}
\usepackage{calc}
\usepackage[simplified]{pgf-umlcd}
\usepackage[section]{placeins}
\usepackage{enumitem}

\newif\ifcomments\commentstrue
\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi
\newcommand{\wss}[1]{\authornote{magenta}{SS}{#1}}
\newcommand{\ds}[1]{\authornote{blue}{DS}{#1}}


\begin{document}



\title{\vspace*{3cm} Test Report for ECA Rules for Ampersand} 
\author{Yuriy Toporovskyy (toporoy)\\ Yash Sapra (sapray) \\ Jaeden Guo (guoy34)}
\date{March 25th,\ 2016} 


\maketitle
\newpage
\vspace*{1cm}
\begin{table}[ht!]\begin{center}
        \caption{Revision History}  
        \begin{tabular}{|c|c|c|}\hline
            \textbf{Author} & \textbf{Date} & \textbf{Comments} \\\hline 
            Yash Sapra & 24 / 03 / 2016 & Initial draft\\\hline

        \end{tabular}
    \end{center}\end{table}
\newpage

\tableofcontents

\newpage

\section{Introduction}\label{intro}
\subsection{Description}

This document details the test results of EFA.
This document uses the test description mentioned in the test plan.
EFA, as well as the core Ampersand system, is
currently in active development where changes occur frequently.
For this reason few tests could not performed. 
A second phase of testing will be performed 
once the EFA project is integrated into the core Ampersand.

\subsection{Scope}
The purpose of this document is to outline the implementation details of the 
EFA project described in the Problem Statement.
EFA is responsible for generating SQL Statements from ECA rules that will 
be used to fixed any violated invariants in the Ampersand prototype. 
The document will serve as a referral document for future software Testing and integration of EFA in the Ampersand project.

%%\clearpage
\printglossaries
\bibliographystyle{alpha}
\bibliography{}

\end{document}

%%  LocalWords:  UML
